\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-02-01 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
  Viscous Instabilities \sep Mobility Ratio \sep Multi-fluid flows \sep Porous media \sep Finite Element Methods. \blue{(choose key-words that do represent the contents of the paper. State-of-the-art development -re key-words should be represented as literature review in the Introduction section.)}

\end{keyword}

@@

\clearpage
%%%         %%%
%%% SECTION %%%
%%%         %%%

%\KCnote{Please reorganise the structure like the papers you read, and reference them!}

\section{Introduction}\label{section:Intro}

@@

@@

\section{Mathematical Formulation}\label{section:math-model}
%\medskip
%\begin{comment}
The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions. In addition, we neglect the effects of capillarity and gravity in our simulations. Therefore the governing equations of conservation of mass and Darcy's law can be described below as,

@@

\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}. Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.
%\end{comment}

@@

%\medskip
\begin{comment}
Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc). However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}. Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}. The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies. 
%=======
%\blue{The Introduction Section of a manuscript is often divided into 4 parts:
%   \begin{enumerate}[(a)]
%       \item Motivation for the work undertaken. What are the environmental, industrial and/or lab problems that this work will help tackling and/or solving (first and \underline{only one} paragraph)? 
%       \item Literature review: this should focus on the main topics directly related to the manuscript (as a rule-of-thumb, you should choose up to 5 key-words that can better represent the work and write \underline{concisely} about recent development on them, i.e., state-of-the-art). Length of literature review should be 3-10 paragraphs and focus on `recent' developments in the topics including strengths and weakness. This `list' of topics (with associated references and range of strengths and weakness) may lead to {\it an explicit statement of the current gap of knowledge on the field that the manuscript will address}. This last key sentence will naturally lead to the;
%       \item Main aim and (list of) objective(s) of the work and how you intend to tackle the science problem (1 paragraph);
%       \item Summary of the work (last paragraph). 
%   \end{enumerate}
%}

>>>>

\begin{keyword} %% keywords here, in the form: keyword \sep keyword
  Viscous Instabilities \sep Mobility Ratio \sep Multi-fluid flows \sep Porous media \sep Finite Element Methods. \blue{(choose key-words that do represent the contents of the paper. State-of-the-art development -re key-words should be represented as literature review in the Introduction section.)}
\end{keyword}

@@

\clearpage

%%%         %%%
%%% SECTION %%%
%%%         %%%
\section{Introduction}\label{section:Intro}

@@

%\blue{The Introduction Section of a manuscript is often divided into 4 parts:
%   \begin{enumerate}[(a)]
%       \item Motivation for the work undertaken. What are the environmental, industrial and/or lab problems that this work will help tackling and/or solving (first and \underline{only one} paragraph)? 
%       \item Literature review: this should focus on the main topics directly related to the manuscript (as a rule-of-thumb, you should choose up to 5 key-words that can better represent the work and write \underline{concisely} about recent development on them, i.e., state-of-the-art). Length of literature review should be 3-10 paragraphs and focus on `recent' developments in the topics including strengths and weakness. This `list' of topics (with associated references and range of strengths and weakness) may lead to {\it an explicit statement of the current gap of knowledge on the field that the manuscript will address}. This last key sentence will naturally lead to the;
%       \item Main aim and (list of) objective(s) of the work and how you intend to tackle the science problem (1 paragraph);
%       \item Summary of the work (last paragraph). 
%   \end{enumerate}
%}

\section{Problem set-up}\label{problem_set_up}

Multiphase flow in porous media is described by mass conversation (or transport) equation and Darcy velovities for each of the phase $\alpha$ ($\alpha$ = g, o, w, for gas, oil, and water phases).
Fingering behaviour is expected to be different from single-phase (piston shape front) due to the effect of different peremeabilities. This will change the mobility contrast between two phases for a given \textit{viscosity} ratio. Because of the  different saturation levels among different layers, eventually this will enhance the flow instabilities.

\subsection{Mathematical Formulation}\label{section:math-model}
%\medskip

@@

The displacing and displaced fluids are considered to be incompressible and immiscible under isothermal and no source or sink conditions. In addition, we neglect the effects of capillarity and gravity in our simulations. Therefore the governing equations of conservation of mass and Darcy's law can be described below as,

@@

\citet{cumming_2011} demonstrated that CVFEM discretisation could also be used to solve Richards' equations (coupled mass conservation and Darcy equation) in heterogeneous media with relatively small computational overhead~\citep[compared with traditional coupled velocity-pressure based formulations, see also][]{cumming_phd2012}. Fluxes over CVs were calculated based upon material properties, whereas the saturation fields were volume-averaged at the interface of the materials, enforcing mass balance as described by \citet{kirkland_1992}.

@@

%\medskip
\begin{comment}
Finite difference methods (FDM) have been extensively used in most industry-standard flow simulators~\citep{aziz_1986, chen_2005, chang_1990} with relative success in multi-physics single phase applications (e.g., black oil model, passive tracer advection etc). However, FDM are often limited to relatively simple geometries (with low grid quality and orientation) representing idealised geological formations~\citep{mlacnik_2004, king_1999}. Additionally, FDM produce excessive numerical dispersion when heterogeneity (represented by permeability and porosity fields) is present~\citep{chavent_1986}. The geometrical flexibility associated with high-order numerical accuracy of finite element methods (FEM) has proven to overcome these deficiencies.
